Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-09 draft.tex
koszul pairing filled in

@@

\subsection{Koszul duality for enveloping $\EE_n$ algebras}

\owen{Use corollary~\ref{cor: koszul dual to main theorem} to exhibit a "dual" Swiss cheese pair and then compute the relative tensor product over the center, which will be the unit $\EE_n$ algebra. Draw a picture of the strip.}

@@

>>>>

\subsection{A Koszul pairing with enveloping $\EE_n$ algebras}

We now briefly remark on how Corollary~\ref{cor: koszul dual to main theorem} lets us see aspects of $\EE_n$-Koszul duality in concrete terms.
Note that $\clies(\fg)$ and $\UU_n(\fg)$ have equivalent $\EE_n$ centers.
If we choose to view $\clies(\fg)$ as an $\EE_n$ algebra in {\em right} modules for ${\frak Z}_n(\fg)$,
then we can consider the relative tensor product
\[
\clies(\fg) \otimes_{{\frak Z}_n(\fg)} \UU_n \fg
\]
and obtain an $\EE_n$ algebra in cochain complexes.
Our models let us show that this relative pairing is trivial, in the following sense.

\begin{lmm}
There is an equivalence  
\[
k \simeq \clies(\fg) \otimes_{{\frak Z}_n(\fg)} \UU_n \fg
\]
of $\EE_n$ algebras.
\end{lmm}

\begin{proof}
Our model $\bZ_n(\fg)$ is an strict associative algebra, and our models $\clies(\Omega^* \otimes \fg)$ and $\bU_n\fg$ are strict right, respectively left, modules over $\bZ_n(\fg)$.
On each open set~$V$, we compute
\begin{align*}
\clies(\Omega^*(V) \otimes \fg) &\otimes^\LL_{\bZ_n(\fg)(V)} \bU_n(V) \\
&\simeq \clies(\Omega^*(V) \otimes \fg) \otimes^\LL_{\Hom^\bullet(\cliels(\Omega^*(V) \otimes \fg, \cliels(\Omega^*_c(V)\otimes \fg))} \cliels(\Omega^*_c(V)\otimes \fg)
\end{align*}
and it is a standard argument to show that this relative tensor product is the unit.
\end{proof}

\owen{Lurie has a beautiful discussion of such pairings somewhere,
so maybe we can borrow his riffs and extend the above in a nice way.}

@@

@@

\owen{Consider referring back to the Koszul pairing (in the calculus section) to talk about Neumann vs Dirichlet boundary conditions.}
